Conditional selectivity for Hexastores

### 2011-07-20 conditional/trunk/selectivity-hexastore.tex
latex fix
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@20 43ef1190-90fd-4dd7-a769-d0121f02b80e

Analogously\todo{anybody good at arguing this mathematically?}, the
conditional selectivity for a triple pattern $T$ can be written as 
\begin{equation}\ref{eq:sel}
sel(T) = sel(S \cap P \cap O) = sel(O | S \cap P) \cdot sel(P | S)
\cdot sel(S) . 
\end{equation}
We note that intersection is commutative, thus similar
relations can be shown for each permutation of terms.

@@

A very simple example is to find the selectivity for the triple pattern
\begin{verbatim}
?person a foaf:Person .
\end{verbatim}
We can easily see that $sel(T) = 2/7$ since two out of the 7 triples
match the pattern. To see how Eq.~\cite{eq:sel} is used, we note that
$sel(S) = 1$ since it is a variable. $sel(P | S) = 2/7$ since the
predicate matches the two occurences of \rdfterm{rdf:type} and the
subject variable doesn't influence this. Finally, $sel(O | S \cap P) =
1$ since the only two occurences of \rdfterm{foaf:Person} occurs in
the same triples as \rdfterm{rdf:type}. Thus, we arrive at the
expected result.

>>>>

Analogously\todo{anybody good at arguing this mathematically?}, the
conditional selectivity for a triple pattern $T$ can be written as 
\begin{equation}\label{eq:sel}
sel(T) = sel(S \cap P \cap O) = sel(O | S \cap P) \cdot sel(P | S)
\cdot sel(S) . 
\end{equation}
We note that intersection is commutative, thus similar
relations can be shown for each permutation of terms.

@@

A very simple example is to find the selectivity for the triple pattern
\begin{verbatim}
?person a foaf:Person .
\end{verbatim}
We can easily see that $sel(T) = 2/7$ since two out of the 7 triples
match the pattern. To see how Eq.~\ref{eq:sel} is used, we note that
$sel(S) = 1$ since it is a variable. $sel(P | S) = 2/7$ since the
predicate matches the two occurences of \rdfterm{rdf:type} and the
subject variable doesn't influence this. Finally, $sel(O | S \cap P) =
1$ since the only two occurences of \rdfterm{foaf:Person} occurs in
the same triples as \rdfterm{rdf:type}. Thus, we arrive at the
expected result.
